### 2023-12-25 README.Rmd
correct zc_diffs() for ACBC - 231225

<li><code>prob_scores()</code>: Converts the raw utilities of a MaxDiff
to choice probabilities by applying the following procedures:

@@

<li><code>zero_anchored()</code></li>: Rescales the raw logits of a
MaxDiff to zero-centered diffs (Chrzan & Orme, 2019, p. 64).

>>>>

<li>

<code>prob_scores()</code>: Converts the raw utilities of a MaxDiff to
choice probabilities by applying the following procedures:

@@

<li><code>zero_anchored()</code></li>

: Rescales the raw logits of a MaxDiff to zero-centered diffs (Chrzan &
Orme, 2019, p. 64).
